Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-04 WSSSPE2_report/WSSSPE2_review.tex
bit more on section 1 - organization of paper

This report extends a previous report that discussed the submission, peer-review, and peer-grouping processes in detail.~\cite{WSSSPE2-pre-report}.  It is also based on a collaborative set
of notes taken through a google doc during the workshop.~\cite{WSSSPE2-google-notes} 
Overall, it discusses the organization work done before the workshop (\S\ref{sec:preworkshop}), the keynotes (\S\ref{sec:keynotes}), \todo{discuss rest of report here...} ... exploring sustainability (\S\ref{sec:exploring}) ... code testing and code review (\S\ref{sec:code_testing})

@@

\note{this section is taken from \cite{WSSSPE2-google-notes}. It could be shortened.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Defining Sustainability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Software Development Experiences}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{Nancy to lead writing of this section}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Credit \& Incentives}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{Dan (OR VOLUNTEER) to lead writing of this section}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Reproducibility \& Reuse \& Sharing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{Neil OR VOLUNTEER to lead writing of this section}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{currently just pre-workshop stuff - needs to be updated}

>>>>

This report extends a previous report that discussed the submission, peer-review, and peer-grouping processes in detail.~\cite{WSSSPE2-pre-report}.  It is also based on a collaborative set
of notes taken through a google doc during the workshop.~\cite{WSSSPE2-google-notes} 
Overall, the report discusses the organization work done before the workshop (\S\ref{sec:preworkshop}), the keynotes (\S\ref{sec:keynotes}), a session on defining sustainability (\S\ref{sec:defining}), the five breakout sessions---exploring sustainability (\S\ref{sec:exploring}); software development experiences (\S\ref{sec:devel}); credit \& incentives (\S\ref{sec:credit}); reproducibility \& reuse \& sharing (\S\ref{sec:reproduce}); code testing \& code review (\S\ref{sec:code_testing})---and some conclusions (\S\ref{sec:conclusions}).  The report also includes an incomplete list of attendees (Appendix \ref{sec:attendees}).

@@

\note{this section is taken from \cite{WSSSPE2-pre-report}. It could be shortened.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Defining Sustainability} \label{sec:defining}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Software Development Experiences} \label{sec:devel}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{Nancy to lead writing of this section}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Credit \& Incentives} \label{sec:credit}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{Dan (OR VOLUNTEER) to lead writing of this section}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Reproducibility \& Reuse \& Sharing} \label{sec:reproduce}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{Neil OR VOLUNTEER to lead writing of this section}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions} \label{sec:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{currently just pre-workshop stuff - needs to be updated}
